### 2020-07-15 README.rmd
Styled.
Badge.

<!-- badges: start -->
[![Build Status](https://travis-ci.org/kaneplusplus/listdown.svg?branch=master)](https://travis-ci.org/kaneplusplus/listdown)
[![AppVeyor build status](https://ci.appveyor.com/api/projects/status/github/kaneplusplus/listdown?branch=master&svg=true)](https://ci.appveyor.com/project/kaneplusplus/listdown)
[![codecov](https://codecov.io/gh/kaneplusplus/listdown/branch/master/graph/badge.svg)](https://codecov.io/gh/kaneplusplus/listdown)
<!-- badges: end -->

@@

The {listdown} package provides functions to programmatically create R Markdown files from 
named lists. It is intended for data analysis pipelines where the presentation of the results
is separated from their creation. For this use case, a data processing (or analysis) is performed
and the results are provided in a single named list, organized heirarchically. With the list and a {listdown} object a workflowr, pdf, word, or html page. List element names denote sections, subsections,
subsubsection, etc. and the list elements contain the data structure to be presented including
graphs and tables. The goal of the package is not to provide a finished, readable document. It is to provide a document with all tables and visualization that will appear (_computational_ components). This serves as a starting point from which a user  can organize outputs, describe a study, discuss results, and provide conclusions (_narrative_ components).

>>>>

<!-- badges: start -->
[![](https://www.r-pkg.org/badges/version/listdown?color=blue)](https://cran.r-project.org/package=listdown)
[![Build Status](https://travis-ci.org/kaneplusplus/listdown.svg?branch=master)](https://travis-ci.org/kaneplusplus/listdown)
[![AppVeyor build status](https://ci.appveyor.com/api/projects/status/github/kaneplusplus/listdown?branch=master&svg=true)](https://ci.appveyor.com/project/kaneplusplus/listdown)
[![codecov](https://codecov.io/gh/kaneplusplus/listdown/branch/master/graph/badge.svg)](https://codecov.io/gh/kaneplusplus/listdown)
[![](http://cranlogs.r-pkg.org/badges/last-month/listdown?color=blue)](https://cran.r-project.org/package=listdown)
<!-- badges: end -->

@@

The {listdown} package provides functions to programmatically create R Markdown files from 
named lists. It is intended for data analysis pipelines where the presentation of the results
is separated from their creation. For this use case, a data processing (or analysis) is performed
and the results are provided in a single named list, organized hierarchically. With the list and a {listdown} object a workflowr, pdf, word, or html page. List element names denote sections, subsections,
subsubsection, etc. and the list elements contain the data structure to be presented including
graphs and tables. The goal of the package is not to provide a finished, readable document. It is to provide a document with all tables and visualization that will appear (_computational_ components). This serves as a starting point from which a user  can organize outputs, describe a study, discuss results, and provide conclusions (_narrative_ components).
